Bounded Model Checking for Embedded Systems \\ (Position Paper)

### 2016-03-18 paper.tex
review verification challenges

State-of-the-art verification methodologies for embedded systems generate test vectors (with constraints), use assertion-based verification, and high-level processor models during simulation~\cite{Behrend15,Lettnin09}; however, embedded system verification also raises additional challenges, such as time and energy constraints, handling of concurrent software, platform restrictions, and legacy designs, which are usually developed with low-level languages. In summary, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system's functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions.
%In summary, the main challenge when verifying embedded systems lies on improving coverage, where more system's functions are verified, and reducing verification time, {\it i.e.}, pruning the state-space exploration during verification. These aspects are of extreme relevance in micro-grids to ensure reliability, which is a key issue for (smart) cities and consumers.

@@

%--------------------------------------
\section{Bounded Model Checking of Embedded Systems}
%--------------------------------------

>>>>

State-of-the-art verification methodologies for embedded systems generate test vectors (with constraints), use assertion-based verification, and high-level processor models during simulation~\cite{Behrend15,Lettnin09}. In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system's functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness; additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints;
	\item handling of concurrent software;
	\item platform restrictions; and
	\item legacy designs.%, which are usually developed with low-level languages.
\end{enumerate}

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices.

%In summary, the main challenge when verifying embedded systems lies on improving coverage, where more system's functions are verified, and reducing verification time, {\it i.e.}, pruning the state-space exploration during verification. These aspects are of extreme relevance in micro-grids to ensure reliability, which is a key issue for (smart) cities and consumers.

@@

%--------------------------------------
\section{Bounded Model Checking for Embedded Systems}
%--------------------------------------
